### 2016-09-08 paper.tex
lots of changes

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{xcolor}
%\usepackage[authordate,bibencoding=auto,strict,backend=biber,natbib]{biblatex-chicago}
\usepackage[round]{natbib}   % omit 'round' option if you prefer square brackets
\bibliographystyle{plainnat}

@@

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand{\Q}{\mathcal{Q}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\x}{\mathbf{x}}
\newcommand{\w}{\theta}
\newcommand{\wkl}{\hat\w^{kl}}
\newcommand{\wave}{\hat\w^{ave}}
\newcommand{\waver}{\hat\w^{ave,r}}
\newcommand{\wboot}{\hat\w^{boot}}
\newcommand{\wmle}{\hat\w^{mle}}
\newcommand{\wmler}{\hat\w^{mle,r}}
\newcommand{\wstar}{{\w^{*}}}
\newcommand{\wq}{\hat\w^{q}}
\newcommand{\wqstar}{\hat\w^{q^*}}
\newcommand{\dist}{\mathcal{D}}

\newcommand{\normal}[2]{\ensuremath{\mathcal{N}\left({{#1}},{{#2}}\right)}}
\newcommand{\trans}[1]{\ensuremath{{#1}^{\mathsf{T}}}}
\newcommand{\ltwo}[1]{{\lVert {#1} \rVert}_2}
\newcommand{\lone}[1]{{\lVert {#1} \rVert}_1}
\newcommand{\lzero}[1]{{\lVert {#1} \rVert}_0}

@@

@@

@@

@@

@@

@@

@@

\section{INTRODUCTION}
We consider the problem of distributed Maximum Likelihood Estimation (MLE) with only a single round of communication.

@@

\section{PROBLEM STATEMENT}

%Let $\dist$ be a distribution over $\mathbb{R}^d$,
%and $X$ a dataset of $N$ points sampled from $\dist$.
%The maximum likelihood estimator for the GLM is
%\begin{equation}
%\wstar=\argmax_\w \int_\dist f(\trans\x\w) + g(\w) dx
%\end{equation}
Let $\X$ be a probability space
and $\Theta$ be the space of model parameters.
Let $f : \X \times \Theta \to \mathbb{R}$ be the likelihood of the data given the model parameters.
Then the true model parameters are given by
\begin{equation}
\wstar = \argmax_\w \int_\X f(\x;\w) d\x
\end{equation}
Since the distribution of $\X$ is typically unknown, $\wstar$ cannot be calculated directly.
Instead, given a sample $X\in\X$, we calculate the MLE by
\begin{equation}
\wmle=\argmax_\w \sum_{\x\in X} f(\x;\w)
\end{equation}
When the dataset $X$ is too large to fit on a single machine,
standard optimization methods cannot calculate $\wmle$ directly.
A number of distributed optimization methods have been created,
but these typically require one round of communication for each iteration of the optimization.
This communication is the main bottleneck of the optimization.

Our goal is to approximate $\wstar$ with only a single round of communication.
Split the dataset $X$ into $m$ disjoint datasets $X_1,...,X_m$ each of size $n=\frac{N}{m}$.
On each machine, solve the \emph{local} maximum likelihood estimate
\begin{equation}
\wmle_i = \argmax_\w \sum_{\x\in X_i} f(\x;\w)
\end{equation}
Solving for $\wmle_i$ requires no communication with other machines.
Next, we need a function $q : \Theta^m \to \Theta$ that combines the parameter estimates from each machine.
Define the resulting parameter estimate as
\begin{equation}
\wq = q(\wmle_1, \wmle_2, ..., \wmle_m)
\end{equation}
Let $\Q$ be the set of all functions from $\Theta^m\to\Theta$,
and $Q$ be a subset of $\Q$.
Our goal is to find the function
\begin{equation}
q^* = \argmin_{q\in Q} \ltwo{\wqstar - \wstar}
\end{equation}

@@

%\section{OUR ALGORITHM}
%
%\section{ANALYSIS}
%
%\section{EXPERIMENTS}
%
%\section{CONCLUSION}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{xcolor}
\usepackage[inline]{enumitem}
%\usepackage[authordate,bibencoding=auto,strict,backend=biber,natbib]{biblatex-chicago}
\usepackage[round]{natbib}   % omit 'round' option if you prefer square brackets
\bibliographystyle{plainnat}

@@

\newtheorem{cor}{Corallary}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\vecspan}{span}
\DeclareMathOperator*{\affspan}{aff}
\DeclareMathOperator*{\tr}{tr}

\newcommand{\zero}{\text{\textbf{0}}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\Y}{\mathcal{Y}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\W}{\mathcal{\hat W}}
\newcommand{\Wave}{{\mathcal{\hat W}^{ave}}}
\newcommand{\Wtave}{{\mathcal{W}^{ave,*}}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\x}{\mathbf{x}}
\newcommand{\w}{\theta}
\newcommand{\wkl}{\hat\w^{kl}}
\newcommand{\wreopt}{\hat\w^{reopt}}
\newcommand{\wave}{\hat\w^{ave}}
\newcommand{\wtave}{\hat\w^{ave,*}}
\newcommand{\waver}{\hat\w^{ave,r}}
\newcommand{\wboot}{\hat\w^{boot}}
\newcommand{\wmle}{\hat\w^{mle}}
\newcommand{\wmler}{\hat\w^{mle,r}}
\newcommand{\wstar}{{\w^{*}}}
\newcommand{\wq}{\hat\w^{q}}
\newcommand{\wqstar}{\hat\w^{q^*}}
\newcommand{\dist}{\mathcal{D}}

\newcommand{\tbias}{t_{\text{\textit{bias}}}}
\newcommand{\tvar}{t_{\text{\textit{var}}}}

\newcommand{\I}{I}
\newcommand{\Iinv}{I^{-1}}
\newcommand{\law}{\ensuremath{\xrightarrow{L}}}
\newcommand{\normal}[2]{\ensuremath{\mathcal{N}\left({{#1}},{{#2}}\right)}}
\newcommand{\trans}[1]{\ensuremath{{#1}^{\mathsf{T}}}}
\newcommand{\ltwo}[1]{{\left\lVert {#1} \right\rVert}_2}
\newcommand{\lone}[1]{{\lVert {#1} \rVert}_1}
\newcommand{\lzero}[1]{{\lVert {#1} \rVert}_0}
\newcommand{\proj}[1]{\pi_{{#1}}}
\newcommand{\prob}[1]{\Pr\left[{#1}\right]}

@@

\newcommand{\ignore}[1]{}
\newcommand{\fixme}[1]{\textbf{FIXME:} {#1}}

@@

@book{lehmann1999elements,
  title={Elements of large-sample theory},
  author={Lehmann, Erich Leo},
  year={1999},
  publisher={Springer Science \& Business Media}
}

@@

@article{dasgupta2003elementary,
  title={An elementary proof of a theorem of {J}ohnson and {L}indenstrauss},
  author={Dasgupta, Sanjoy and Gupta, Anupam},
  journal={Random Structures \& Algorithms},
  volume={22},
  number={1},
  pages={60--65},
  year={2003},
  publisher={Wiley Online Library}
}

@article{matouvsek2008variants,
  title={On variants of the {J}ohnson--{L}indenstrauss lemma},
  author={Matou{\v{s}}ek, Ji{\v{r}}{\'\i}},
  journal={Random Structures \& Algorithms},
  volume={33},
  number={2},
  pages={142--156},
  year={2008},
  publisher={Wiley Online Library}
}

@@

@article{spokoiny2012parametric,
  title={Parametric estimation. Finite sample theory},
  author={Spokoiny, Vladimir},
  journal={The Annals of Statistics},
  volume={40},
  number={6},
  pages={2877--2909},
  year={2012},
  publisher={Institute of Mathematical Statistics}
}

@@

@article{hsu2012tail,
  title={A tail inequality for quadratic forms of subgaussian random vectors},
  author={Hsu, Daniel and Kakade, Sham M and Zhang, Tong and others},
  journal={Electron. Commun. Probab},
  volume={17},
  number={52},
  pages={1--6},
  year={2012}
}

@@

@book{shalev2014understanding,
  title={Understanding machine learning: From theory to algorithms},
  author={Shalev-Shwartz, Shai and Ben-David, Shai},
  year={2014},
  publisher={Cambridge University Press}
}

@@

\section{INTRODUCTION}
We consider the problem of distributed Maximum Likelihood Estimation (MLE).

@@

\subsection{Problem Statement}

%Let $\Theta\subseteq\mathbb{R}^d$ be the parameter space,
%$\X\subseteq\mathbb{R}^d$ be the covariate space,
%and $\Y\subseteq\mathbb{R}$ be the response space.
%Let $Z\subset\X\times\Y$ be a set of $mn$ i.i.d. datapoints.
%Then the centralized Maximum Likelihood Estimator (MLE) is defined as
%\begin{equation}
%\wmle = \argmax_\w \sum_{(\x,y)\in Z} f(y-\trans\x\w)
%\end{equation}

Let $\Y\subseteq\mathbb{R}$ be the space of response variables,
$X\subseteq\mathbb{R}^d$ be the space of the covariates,
and $\Theta\subseteq\mathbb{R}^d$ be the parameter space.
We assume a linear model.
The log-likelihood of data point $(\x,y)\in\X\times\Y$ given the model's true parameter $\wstar\in\Theta$ is denoted by $f(y,\trans\x\wstar)$.
%\begin{equation}
%y = g^{-1}(\trans\x\wstar)
%\end{equation}
%Here, $g : \mathbb{R} \to \mathbb{R}$ is the link function and $\wstar\in\Theta\subseteq\mathbb{R}^d$ is the true parameter of our model.
Let $Z\subset\X\times\Y$ be a dataset of $mn$ i.i.d. observations.
Then the maximum likelihood estimator is
\begin{equation}
%\wmle=\argmax_\w \sum_{i=1}^{nm} g(y_i-\trans\x_i\w)
\wmle=\argmax_\w \sum_{(\x,y)\in Z} f(y,\trans\x\w)
\end{equation}
Assume that $Z$ has been split up onto $m$ machines so that each machine $i$ has dataset $Z_i$ of size $n$, and all the $Z_i$ are disjoint.
Then each machine calculates the local estimator
\begin{equation}
\wmle_i = \argmax_\w \sum_{(\x,y) \in Z_i} f(y,\trans\x\w)
\end{equation}
Solving for $\wmle_i$ requires no communication with other machines.
Our goal is to provide a function $q : \Theta^m \to \Theta$ that ``merges'' these estimates.
The resulting merged estimate should have error as close to $\wmle$ as possible.

%Next, we need a function $q : \Theta^m \to \Theta$ that combines the parameter estimates from each machine.
%Define the resulting parameter estimate as
%\begin{equation}
%\wq = q(\wmle_1, \wmle_2, ..., \wmle_m)
%\end{equation}
%Let $\Q$ be the set of all functions from $\Theta^m\to\Theta$,
%and $Q$ be a subset of $\Q$.
%Our goal is to find the function
%\begin{equation}
%q^* = \argmin_{q\in Q} \ltwo{\wqstar - \wstar}
%\end{equation}

\subsection{Proposed Solution}

The averaging estimator is defined as
\begin{equation}
\wave = \frac{1}{m}\sum_{i=1}^m \wmle_i
\end{equation}
Define the matrix $\hat W : \mathbb{R}^{d\times m}$ to have $i$th column equal $\wmle_i-\wave$.
Then our estimator is defined as
\begin{equation}
\begin{aligned}
\hat\alpha &= \argmax_\alpha \sum _{(\x,y)\in Z^{reopt}} f\left(y,\trans\x (\hat W\alpha + \wave)\right)
\\
\wreopt &= \hat W \hat\alpha + \wave
\end{aligned}
\end{equation}
where $Z^{reopt}$ is a small dataset of size $O(m)$.
In the analysis of this estimator, we assume that $Z^{reopt}$ is independent of the $\wmle_i$;
that is, the data points in $Z^{reopt}$ were not used in the single machine optimizations.
In practice, however, this restriction is not necessary.

This estimator has the following intuitive interpretation.
We use the $\wmle_i$ estimates from the first round of communication to create a subspace $\Wave=\affspan\{\wave\}\cup{\{\wmle\}}_{i=1}^m$.
Then in the second round of optimization, we project all of our data points down into this subspace.
Because this subspace is small, we need only a small number of data points to get a good estimate of the optimum.
Because of the way we constructed $\Wave$,
the optimum in $\Wave$ will be close to the true optimum.
%The true parameter $\wstar$ should be close to this subspace.
%In the first round of optimization (determining the $\wmle_i$s),
%we're actually finding a subspace
%The estimator $\wreopt$ lives in a subs

\newpage
\section{ANALYSIS}

\subsection{Notation}

\subsection{Few data points are needed}
\label{sec:vcdim}

Define the space
$\Wave=\affspan\{\wave_i\}_{i=1}^m\cup\{\wave\}$.
Define $L : \mathbb{R} \to \mathbb{R}$ to be the 0-1 loss over the true data distribution.

\begin{theorem}
Let $\w^\Wave$ be an arbitrary point in $\Wave$ and $\delta\in(0,1)$.
Then with probability at least $1-\delta$,
\begin{equation}
L(\wreopt) \le L(\w^\Wave) + O\left(\sqrt{\frac{m + \log(1/\delta)}{n^{reopt}}}\right)
\end{equation}
\end{theorem}
\begin{proof}
For each machine $i$, fix the set of data points $Z_i$.
This in turn fixes the $\wmle_i$ and the space $\Wave$.
The hypothesis class defined by $\Wave$ has VC dimension $m$ because it is linear with $m$ parameters.
Since each of the data points in $Z^{reopt}$ is independent of $\Wave$,
the result follows immediately from standard VC theory.
See for example Chapter 6 of \cite{shalev2014understanding}.
%
%\fixme{
    %Need to rework the definitions in Section 1 so that the data points in the second optimization don't depend on the first optimization.
%}
\end{proof}

\subsection{In the Normal Regime}
\label{sec:normal}

\subsubsection{Assumptions}

We assume that for every estimator $\hat\w$ trained on $n$ data points,
\begin{equation}
\label{eq:assumption}
\hat\w - \E\hat\w \sim \frac{1}{\sqrt n}\normal{\zero}{I^{-1}_{\E\hat\w}}
%\hat\w \sim \normal{\E\hat\w}{\frac{1}{n}I^{-1}_{\E\hat\w}}
\end{equation}
%
%Throughout Section \ref{sec:normal} we assume that $\wave_i$ is normally distributed with mean $\wtave$ and covariance $\frac{1}{n}I^{-1}_{\wtave}$.
%\begin{equation}
%\label{eq:assumption}
%\wmle_i \sim \normal{\E\wmle_i}{\frac{1}{n}I^{-1}_{\E\wmle_i}}
%\end{equation}
%Here, $I_{\wtave}$ is the Fisher information matrix at point $\wtave$.
Here, $I_{\E\hat\w}$ is the Fisher information matrix for parameter $\E\hat\w$.
This assumption is motivated by the central limit theorem for maximum likelihood estimation.
%There are many versions of this theorem.
Theorem 7.5.2 of \cite{lehmann1999elements} is particularly simple version and reproduced below.
\begin{theorem}
\label{thm:clt}
Assume the following mild regularity conditions:
\begin{enumerate}[noitemsep,topsep=0pt]%,label=(\itshape\roman*)]
\item all data points in $Z_i$ are i.i.d.;
\item the parameter space $\Theta$ is open;
\item the model is identifiable and consistent;
\item the matrix $\I_{\wtave}$ is non-singular;
\item the support set $A = \{(y,\x) : f(y,\x;\theta) > 0\}$ is independent of $\theta$;
and \item for all $(y,\x)\in A$, $f(y,\x;\theta)$ is three times differentiable with respect to $\theta$,
and the third derivative is continuous.
\end{enumerate}
Then in the limit as $n\to\infty$,
\begin{equation*}
\wave_i \law \wtave + \frac{1}{\sqrt n} \normal{0}{\Iinv_\wstar}
\end{equation*}
Here the notation $\law$ denotes convergence in law,
which is the standard notion of convergence for a sequence of probability distributions.
\end{theorem}

Note that Theorem \ref{thm:clt} does not require the likelihood $f$ to be convex.

There are many generalizations of Theorem \ref{thm:clt}.
For example, Theorem 4.2 in \cite{spokoiny2012parametric} provides finite sample bounds with explicit dependence on the degree of model misspecification, optimization error, and the lack of independence in the data variables.
Because Spokoiny's theorem is non-asymptotic, the theorem that the estimator is a sub-Gaussian random variable.

\subsubsection{Analyzing $\wave$}

We provide a simple bound that shows that averaging does not improve the bias of our estimator,
but reduces the variance at the rate $O((nm)^{-1})$.
This bound is well known, but our analysis is significantly simpler and provides a sharp, easy to interpret constant factor.
The main idea of our technique is to show that the variance is normally distributed.
The ideas in this proof will be used in Section \ref{sec:analreopt} where we show that the variance of $\wreopt$ is the same as $\wave$, but that the bias is reduced.

\begin{theorem}
Let $t>0$.
Then with probability at least $1-\exp(-t)$,
\begin{equation}
\ltwo{\wstar-\wave}^2 \le \ltwo{\wstar-\E\wmle_i}^2 + \frac{v_t}{mn}
\end{equation}
where
\begin{equation}
v_t =
\tr{\Iinv_{\wtave}}
+ 2\sqrt{\tr ({\I^{-2}_{\wtave}})t}
+ 2\ltwo{\Iinv_{\wtave}}t
\end{equation}
\end{theorem}
\begin{proof}
It is well known that the MSE of an estimator is the sum of its bias and variance.
That is,
\begin{equation}
\ltwo{\wstar-\wave}^2 = \ltwo{\wstar-\E\wave}^2 + \ltwo{\E\wave-\wave}^2
\label{eq:biasvar}
\end{equation}
By the linearity of expectation, we have that
\begin{align}
\E\wave
&=
\E\frac{1}{m}\sum_{i=1}^m\wmle_i
%\\&=
=
\frac{1}{m}\sum_{i=1}^m\E\wmle_i
=
\E\wmle_i
\label{eq:expwave}
\end{align}
and so the bias
$\ltwo{\wstar-\E\wave}
=
\ltwo{\wstar-\E\wmle_i}
$.
Next, we see that the variance is a Gaussian random variable.
We have by Equations \ref{eq:expwave} and \ref{eq:assumption} that
\begin{align}
\wave-\E\wave
&=
\frac{1}{m}\sum_{i=1}^m\left(\wmle_i-\E\wave\right)
\\&=
\frac{1}{m}\sum_{i=1}^m\left(\wmle_i-\E\wmle_i\right)
\\&\sim
\frac{1}{m}\sum_{i=1}^m\left(\frac{1}{\sqrt n}\normal\zero{I^{-1}_{\E\wave}}\right)
\\&=
\frac{1}{\sqrt {nm}}\normal\zero{I^{-1}_{\E\wave}}
%\\&\sim
%\frac{1}{m}\normal{m\E\wmle_i}{\frac{m}{n}I^{-1}}
%\\&\sim
%\normal{\E\wmle_i}{\frac{1}{nm}I^{-1}}
%\\
%\wave-\E\wmle_i
%&\sim
%\normal{\zero}{\frac{1}{nm}I^{-1}}
%\\
%\wave-\E\wave
%&\sim
\end{align}
%Centering the distribution and applying Equation \ref{eq:expwave} gives
%\begin{equation}
%\E\wave-\wave
%\sim
%\normal{\zero}{\frac{1}{nm}I^{-1}}
%\end{equation}
So bounding the variance reduces to bounding the norm of a Gaussian.
Applying the bound in Proposition 1.1 from \cite{hsu2012tail} gives that with probability at least $1-\exp(-t)$,
\begin{equation}
\ltwo{\E\wave-\wave}^2 \le \frac{v_t}{\sqrt{nm}}
\label{eq:ct1}
\end{equation}
%where
%\begin{equation}
%\begin{aligned}
%v_t'
   %= \tr\left({\frac{1}{mn}\I^{-1}_{\wtave}}\right)
%+ 2&\sqrt{\tr \left({\frac{1}{mn}\I^{-1}_{\wtave}}\right)^2t}&
%\\+ 2\ltwo{\frac{1}{nm}\I^{-1}_{\wtave}}t&
%\end{aligned}
%\end{equation}
%Then by the linearity of trace and scalability of norms,
%\begin{equation}
%v_t' =
%\frac{1}{mn}\left(
%\tr\I^{-1}_{\wtave}
%+ 2\sqrt{\tr \I^{-2}_{\wtave}t}
%+ 2\ltwo{\I^{-1}_{\wtave}}t
%\right)
%\label{eq:ct2}
%\end{equation}
Substituting Equations \ref{eq:expwave} and \ref{eq:ct1} into Equation \ref{eq:biasvar} gives the stated result.

\end{proof}

%\begin{theorem}
%Let $t>0$.
%Then with probability at least $1-\exp(-t)$,
%\begin{equation}
%\ltwo{\wave-\wtave} \le \sqrt{\frac{v_t}{mn}}
%\end{equation}
%where
%\begin{equation}
%v_t =
%\tr{\Iinv_{\wtave}}
%+ 2\sqrt{\tr ({\I^{-2}_{\wtave}})t}
%+ 2\ltwo{\Iinv_{\wtave}}t
%\end{equation}
%\end{theorem}

%\begin{proof}
%By our assumption above, we have that
%\begin{equation}
%\wave \sim \wtave+\normal{0}{\frac{1}{nm}I^{-1}_{\wtave}}
%\end{equation}
%which implies
%\begin{equation}
%\wave - \wtave \sim \normal{0}{\frac{1}{nm}I^{-1}_{\wtave}}
%\end{equation}
%So our problem reduces to bounding the norm of a Gaussian random variable.
%Applying the bound in Proposition 1.1 from \cite{hsu2012tail} gives the stated result.
%\end{proof}

%\ignore{
%We introduce the following lemma due to \cite{hsu2012tail} for bounding the norm of a Gaussian random variable.
%\begin{lemma}
%\label{lemma:hsu}
%Let $\x\in\mathbb{R}^d$ be an isotropic multivariate Gaussian random vector with zero mean.
%Let $\trans A A = \Sigma$ be the covariance matrix of random vector $A\x$.
%For all $t>0$,
%\begin{equation}
%\prob{\ltwo{A\x}^2 > \tr{\Sigma} + 2\sqrt{\tr (\Sigma^2)t} + 2\ltwo{\Sigma}t}
%\le
%\exp(-t)
%\end{equation}
%\end{lemma}
%A straightforward application of this lemma gives us that with probability at least $1 - \exp(-\tvar)$,
%\begin{equation}
%\begin{split}
%%\prob{
%&\ltwo{\wave-\wtave}
%\\
%&\le
%\sqrt{
    %\frac{1}{m}
    %\left(\tr{\Iinv_{\wtave}}
        %+ 2\sqrt{\tr ({\Iinv_{\wtave}}^2)\tvar}
        %+ 2\ltwo{\Iinv_{\wtave}}\tvar
    %\right)
%}
%%}
%\end{split}
%\end{equation}
%}

\subsection{Analyzing $\wreopt$}
\label{sec:analreopt}

We now extend the analysis of the previous section to the $\wreopt$ estimator.
We show that its variance is bounded by the variance of $\wave$,
but that the bias shrinks as $O(1-m/d)$.

Recall from Section \ref{sec:vcdim} that the estimator $\wreopt$ has low error with high probability compared to any parameters in the space $\Wave$.
Denote by $\proj\Wave$ the projection operator onto the space $\Wave$.
In this section, we analyze the bias and variance of $\proj\Wave\wstar$.

\begin{theorem}
Let $t>0$.
Then we have that
\begin{equation}
\ltwo{\wstar-\proj\Wave\wstar}
\le
b_t\sqrt{\left(1-\frac{m}{d}\right)}
+
\sqrt\frac{v_{t}}{nm}
\end{equation}
where
\begin{equation}
b_t = \ltwo{\wstar-\E\wmle_i}\sqrt{t + 1}
\end{equation}
with probability at least $1-\exp (-\frac{b}{2} (\tbias-\ln(\tbias+1)))$,
and $v_t$ is defined as in Theorem \ref{thm:}, Equation \ref{eq:} with probability at least $1-\exp(-t)$.
\end{theorem}
%Define the spaces
%\begin{align}
%\W&=\vecspan\{\wmle_i - \wave\}_{i=1}^m\\
%\Wave&=\affspan\{\wave_i\}_{i=1}^m\cup\{\wave\}\\
%\Wtave&=\affspan\{\wave_i\}_{=1}^m\cup\{\wtave\}
%%\Wave&=\vecspan\{\wave_i-\wave\}_{i=1}^m\\
%%\Wtave&=\vecspan\{\wave_i-\wtave\}_{i=1}^m
%\end{align}
%Denote by $\proj\A$ to be the projection operator onto the space $\A$.
%Denote by $I_\w$ the Fischer information matrix at the point $\w$.

\ignore{
\begin{theorem}
%Assume that $n$ is large enough that $\wmle_i$ is distributed according to $\normal{\wtave}{\Iinv_{\wtave}}$.
%Let $\delta\in(0,1)$.
%Then with probability at least $1-\delta$,
We have that
\begin{equation}
\ltwo{\wstar-\proj\Wave\wstar}
\le \epsilon_{bias} + \epsilon_{var}
\end{equation}
where for all $\tbias>0$,
\begin{equation*}
%\begin{split}
%\prob{
    \epsilon_{bias}
    \le
    \ltwo{\wstar-\wtave}\sqrt{(\tbias + 1)\left(1-\frac{m}{d}\right)}
%}
%\\
%\ge
%1-\exp \bigg(-\frac{b}{2} (\beta-\ln(\beta+1))\bigg)~~&
%\end{split}
\end{equation*}
with probability at least
$1-\exp (-\frac{b}{2} (\tbias-\ln(\tbias+1)))$
and for all $\tvar>0$,
\begin{equation*}
\begin{split}
&\epsilon_{var}
\\
&\le
\sqrt{
    \frac{1}{m}
    \left(\tr{\Iinv_{\wtave}}
        + 2\sqrt{\tr ({I^{-2}_{\wtave}})\tvar}
        + 2\ltwo{\Iinv_{\wtave}}\tvar
    \right)
}
\end{split}
\end{equation*}
with probability at least $1-\exp(-\tvar)$.

%\begin{equation}
%\begin{split}
%&\ltwo{\wstar-\proj\Wave\wstar}
%\\
%&\le
%\ltwo{\wstar-\wtave}\sqrt{(\beta + 1)\left(1-\frac{m}{d}\right)}
%\\
%&+
%\sqrt{
    %\frac{1}{m}
    %\left(\tr{\Iinv_{\wtave}}
        %+ 2\sqrt{\tr ({\Iinv_{\wtave}}^2)t}
        %+ 2\ltwo{\Iinv_{\wtave}}t
    %\right)
%}
%\le
%\exp \bigg(-\frac{b}{2} (\beta-\ln(\beta+1))\bigg)~~&
%\end{split}
%\end{equation}
\end{theorem}
}

\begin{proof}
Note that the space $\Wave$ depends on the data.
Therefore, we can think of $\proj\Wave\wstar$ as an estimator of $\wstar$.
As in the proof of Theorem \ref{thm:},
we begin by decomposing the MSE into its bias and variance components.
\begin{equation}
\begin{split}
\ltwo{\wstar-\proj\Wave\wstar}^2
&=
\ltwo{\wstar-\E\proj\Wave\wstar}^2
\\&+
\ltwo{\E\proj\Wave\wstar-\proj\Wave\wstar}^2
\end{split}
\end{equation}
%Define $\Wtave = \vecspan\{\wmle_i-\wtave\}_{i=1}^m$.
%Then,
We have that
\begin{align}
\ltwo{\wstar-\proj\Wave\wstar}
&\le
\ltwo{\wstar-\proj\Wtave\wstar}
+
\ltwo{\proj\Wtave\wstar-\proj\Wave\wstar}
\\
&=
\ltwo{\wstar-\proj\Wtave\wstar}
+
\ltwo{\wave-\wtave}
\label{eq:errdecomp}
\end{align}
The first line follows from the triangle inequality.
The second line follows because every point in $\Wtave$ is a translation of a point in $\Wave$ by the vector $\wave-\wtave$.

%\begin{lemma}
%Let $a$ and $b$ be integers with $b<a$.
%Let $\x$ be a random vector on the $a$ dimensional unit sphere.
%Let $T : \mathbb{R}^a \to \mathbb{R}^b$ be the projection operator that preserves the first $b$ coordinates of a vector and drops the rest.
%Then for all $\beta>0$,
%\begin{equation}
%\prob{\ltwo{T\x} \ge \sqrt{(\beta + 1)\frac{b}{a}}}
%\le
%\exp \left(\frac{b}{2}(-\beta+\ln(\beta+1))\right)
%\end{equation}
%\end{lemma}
We will now bound the two terms in Equation \ref{eq:errdecomp} separately.
To bound the left term, we introduce the following lemma.
It is adapted from Lemma 2.2 in \cite{dasgupta2003elementary}.
It has been simplified to ignore cases irrelevant for our purpose.
\begin{lemma}
Let $a$ and $b$ be integers with $b<a$.
Let $\x\in\mathbb{R}^a$ be an arbitrary vector.
Let $T : \mathbb{R}^a \to \mathbb{R}^b$ be projection onto a subspace of size $b$ distributed uniformly at random.
Then for all $\beta>0$,
\begin{equation}
\begin{split}
\prob{\ltwo{T\x} \ge \ltwo\x\sqrt{(\beta + 1)\frac{b}{a}}}&
\\
\le
\exp \bigg(-\frac{b}{2} & (\beta-\ln(\beta+1))\bigg)
\end{split}
\end{equation}
\end{lemma}
To apply this lemma, note that $\proj\Wtave$ is not a linear projection but an affine projection.
We first apply a translation so that we are working with the linear projection $\proj\W$.
\begin{align}
\ltwo{\wstar-\proj\Wtave\wstar}
&=
\ltwo{(\wstar-\wtave)-\proj\W(\wstar-\wtave)}
\\
&=
\ltwo{(I-\proj\W)(\wstar-\wtave)}
\end{align}
Now, $(I-\proj\W)$ is a random projection onto a subspace of dimension $d-m$.
(\fixme{This projection is not chosen uniformly at random because the covariance of $\wmle_i$ is not the identity.})
This gives us that for all $\tbias>0$,
\begin{equation}
\begin{split}
\prob{\ltwo{\wstar-\proj\Wtave\wstar} \ge \ltwo{\wstar-\wtave}\sqrt{(\tbias + 1)\left(1-\frac{m}{d}\right)}}&
\\
\le
\exp \bigg(-\frac{b}{2} (\tbias-\ln(\tbias+1))\bigg)~~&
\end{split}
\end{equation}

\end{proof}

%The following lemma is adapted from Theorem 3.1 in \cite{matouvsek2008variants}.
%It has been simplified to ignore cases irrelevant for our purpose.
%\begin{lemma}
%Let $a$ and $b$ be integers with $a>b$.
%Let $T\in\mathbb{R}^{a\times b}$ be a random matrix with entries drawn i.i.d. from the standard normal distribution.
%Let $\x\in\mathbb{R}^a$ be an arbitrary vector.
%Then there exists a constant $c$ such that for all $\delta\in(0,1)$,
%\begin{equation*}
%\prob{\ltwo{T\x} \le \left(\sqrt{b}+c\sqrt{\log\frac{\delta}{2}}\right)\ltwo\x} \le 1-\delta
%\end{equation*}
%\end{lemma}

%\begin{cor}
%%Assume that Conditions (1-5) hold.
%%Then as $n\to\infty$,
%%\begin{enumerate}
%%\item
%If $f$ is locally $\sigma$-strongly convex,
%\begin{equation}
%\ltwo{\wstar-\wreopt} \le
%\end{equation}
%%\end{enumerate}
%\end{cor}
%
%\begin{proof}
%\end{proof}

%\subsection{Proposed Solution}
%
%We propose the following solution.
%Define the matrix $W : \mathbb{R}^{d\times m}$ to have $i$th column equal $\wmle_i$.
%%That is,
%%\begin{equation}
%%W = (\wmle_1, \wmle_2, ..., \wmle_m)
%%\end{equation}
%Then our estimator is defined as
%\begin{equation}
%\begin{aligned}
%\alpha &= \argmax_\w \sum _{(\x,y)\in Z_i} f(y,\trans\x W\w)
%\\
%\w &= \trans W \alpha
%\end{aligned}
%\end{equation}
%Note that the inner $\w$ above is a vector of dimension $m$, not $d$ (as elsewhere).
%In words
%%In words, this estimator takes the data set $Z'$ and projects it onto the subspace spanned by the

\newpage

\clearpage

@@

\newpage
\ignore{
\section{ANALYSIS}

First we justify why only a small number of data points is needed for the second optimization.
For simplicity, we'll restrict our discussion to the case of binary classification.
This lets us use standard VC-dimension arguments.

\subsection{Few datapoints are needed in the optimization}

%Recall the following theorem from standard VC theory.
%\begin{theorem}
%Let $Z$ be a dataset of $n$ points sampled i.i.d. from distribution $\D$.
%Let $\wmle$ be the parameters of the maximum likelihood estimator of $Z$.
%Let $L : \Theta \to \mathbb{R}$ be the true 0-1 loss on the distribution $\D$.
%Let $d$ be the VC dimension of the hypothesis class $\Theta$.
%Then with probability at least $1-\delta$,
%\begin{equation}
%L(\wmle) \le L(\wstar) + O\left(\sqrt{\frac{d + \log(1/\delta)}{n}}\right)
%\end{equation}
%\end{theorem}
%For an extended discussion of the above theorem,
%see for example Chapter 6 of \cite{shalev2014understanding}.
\begin{theorem}
%Let $\Y=\{0,1\}$.
Define $\alpha^{*}$ to be the optimal parameter constrained to the space spanned by the columns of $W$.
In notation,
\begin{equation}
\alpha^{*} = \argmax_{\alpha} \int_{\Y\times\X} f(y,\trans\x W\alpha) d(y,\x)
\end{equation}
Define $L : \mathbb{R} \to \mathbb{R}$ to be the 0-1 loss over the true data distribution.
Then with probability at least $1-\delta$,
\begin{equation}
L(\alpha^*) \le L(\alpha) + O\left(\sqrt{\frac{m + \log(1/\delta)}{n^{reopt}}}\right)
\end{equation}
\end{theorem}
\begin{proof}
For each machine $i$, fix the set of data points $Z_i$
(which in turn fixes the $\wmle_i$).
Define $\A$ to be the space of parameters
\begin{equation}
\A=\{\trans W\w : \w \in \Theta\}
\end{equation}
The linear hypothesis class defined by $\A$ has VC dimension $m$.
Since each of the data points in $Z^{reopt}$ is independent of $W$,
the result follows immediately from standard VC theory.
See for example Chapter 6 of \cite{shalev2014understanding}.
\end{proof}

\begin{theorem}

\end{theorem}

\ignore{
\subsection{Overall growth}

In this section we assume the following regularity conditions.
